Seminar paper on Probabilistic Near-Duplicate Detection Using Simhash

### 2019-07-09 ii/paper/paper.tex
More text

$\prec$ represents the lexicographical comparison operator on ${S}$. Lemma 1 describes that two sets $S_1 \prec S_2$, if there exists an index $i < h$ such that both sets have the same leading elements of length $i$, but $S_2$ is still larger in the $(i+1)$th element.

\begin{figure}[H]
\includegraphics[scale=0.4]{./gfx/vosh_algorithm.png}
\centering
\caption{Pseudocode representation for the generation of a Volatility Ordered Set Heap (VOSH).}\label{fig:weight-distribution}
\end{figure}

\begin{figure}[H]
\includegraphics[scale=0.4]{./gfx/vosh_structure.png}
\centering
\caption{Example for a generated VOSH structure generated by Algorithm 2.}\label{fig:weight-distribution}
\end{figure}

@@

\section{Relevance as of 2019}
Near duplicate detection is still a very important research field.
The current trend shows, that data will continue to be generated in a exponential manner.

For instance, Google started using \emph{simhash} in 2007 for their web-crawling services~\cite{Manku:2007:DNW:1242572.1242592}.
With Google being one of the biggest Internet companies and the number one search engine, relevance of this topic is obviously very high.

>>>>

$\prec$ represents the lexicographical comparison operator on ${S}$. Lemma 1 describes that two sets fulfill $S_1 \prec S_2$, if there exists an index $i < h$ such that both sets have the same leading elements of length $i$, but $S_2$ is still larger in the $(i+1)$th element.

\begin{figure}[H]
\includegraphics[scale=0.4]{./gfx/vosh_algorithm.png}
\centering
\caption{Pseudocode representation for the generation of a Volatility Ordered Set Heap (VOSH).}\label{fig:vosh-algorithm}
\end{figure}

\begin{figure}[H]
\includegraphics[scale=0.4]{./gfx/vosh_structure.png}
\centering
\caption{Example for a generated VOSH structure generated by Algorithm 2.}\label{fig:vosh-structure}
\end{figure}

The assertions gained by Lemma 1 allow us to create an algorithm, that creates a space efficient lookup data structure for determining near-duplicates within a certain Hamming distance $h$.
The bit combinations are sorted using the algorithm visualized in figure~\ref{fig:vosh-algorithm}.

The algorithm creates a binary tree structure, which is generated as follows.
For each node, check, whether the rightmost bit can be incremented.
If that is the case, create a new node with the new bit constellation as the left child node.
If the bit cannot be incremented, the left child node will be omitted.

At the same time, check the bits from right to left whether there exists a difference (or gap) between two adjacent bits that equals 2.
If there exists such a gap, the left bit of those two bits is incremented.
The new bit constellation now forms the right child node.
If there is no such gap, the right child node is simply omitted.

Figure~\ref{fig:vosh-structure} shows example results for volatility heaps created by this algorithm.
The volatility heaps are created with different Hamming distance thresholds $h$.

\section{Probabilistic Search}

@@

\section{Relevance as of 2019}
Near duplicate detection is still a very important research field.
The current trend shows, that data will continue to be generated in a exponential manner.
Tackling an even larger amount of data and filtering it for duplicates will continue to create new challenges in respect to data throughput and RAM limitations.

Simhash is being used by many companies in various application fields.
For instance, Google started using \emph{simhash} in 2007 for their web-crawling services~\cite{Manku:2007:DNW:1242572.1242592}.
With Google being one of the biggest Internet companies and the number one search engine, relevance of this topic is obviously very high.

This is especially interesting, since this paper takes the original algorithm proposed for usage in Googles web crawler~\cite{Manku:2007:DNW:1242572.1242592} as comparison for their own research while showing that they are capable of significantly speeding up the lookup.
